---
title: "bs"
output: html_document
---

```{r}

install.packages("bsgof")
```

```{r}

library(bsgof)
library(MASS)
library(survival)
#library(gbs)
library(stats)
library(stats4)
library(boot)
library(locfit)
library(flexsurv)
library(lattice)
library(HSAUR)
```

### Unconditional Survival Function of the BS frailty model

```{r}

uncsurv_BS <- function(t,delta,lambda){
  st <- (exp( (delta/2)*( 1 - sqrt((delta+4*lambda*t+1)/(delta+1)) ) )*(sqrt(delta+1) + sqrt((delta+4*lambda*t+1)) ))/(2*sqrt(delta+4*lambda*t+1))
  
  return(st)
}
```

### Unconditional Hazard Function of the BS frailty model

```{r}

unchazd_BS <- function(t,delta,lambda){
  
  ht <- lambda*( delta*( delta + sqrt( (delta+1)*(delta+4*lambda*t+1) ) + 4*lambda*t + 3 ) + 2 )/( (delta+4*lambda*t+1)*( delta + sqrt( (delta+1)*(delta+4*lambda*t+1) ) + 1) )
  
  return(ht)
  
}
```

### Log Likelihood Function of BS Frailty Model (Exp - baseline)

```{r}

log.lik_BS <- function(par,x,cens){
  
  delta   <- par[1]
  lambda  <- par[2]
  bad     <- 1e100

  if (any(!is.finite(c(delta,lambda))) || delta <= 0 || lambda <= 0) {
    return(bad)
  }

  sf <- uncsurv_BS(t=x,delta=delta,lambda=lambda)
  hz <- unchazd_BS(t=x,delta=delta,lambda=lambda)

  if (any(!is.finite(sf)) || any(!is.finite(hz)) || any(sf <= 0) || any(hz <= 0)) {
    return(bad)
  }
  
  loglik <- sum(log(sf)) + sum(cens*log(hz))

  if (!is.finite(loglik)) {
    return(bad)
  }
  
  return (-loglik)
}

log.lik_BSHE <- function(par,y,cens){
  
  loglik <- -log.lik_BS(par=par,x=y,cens=cens)
  
  return (loglik)
}

```

### Cumulative Hazard Rate baseline - Weibull

```{r}

CHR_base <- function(t,alpha,eta){
  
  chr <- (t/alpha)^eta
  
  return(chr)
}
```

### Hazard Rate baseline - Weibull

```{r}

HR_base <- function(t,alpha,eta){
  
  hr <- (eta*(t^(eta-1)))/(alpha^eta)
  return(hr)
}
```

### Unconditional survival function of BS frailty

```{r}

unc_sf <- function(t,alpha,eta,delta){
  
  a <- sqrt(delta+4*CHR_base(t,alpha,eta)+1)
  b <- (delta/2)*(1 - (a/sqrt(delta+1)) )
  c <- a + sqrt(delta + 1)
  
  usf <- (exp(b)*c)/(2*a)
  
  return(usf)
  
}

```

### Unconditional hazard rate of BS frailty

```{r}

unc_hz <- function(t,alpha,eta,delta){
  
  a <- delta*(delta + sqrt( (delta+4*CHR_base(t,alpha,eta)+1)*(delta+1) ) + 4*CHR_base(t,alpha,eta) + 3) + 2
  b <- (delta + sqrt( (delta+4*CHR_base(t,alpha,eta)+1)*(delta+1) ) + 1)
  
  uhr <- ( (HR_base(t,alpha,eta))*a )/ ( (delta+4*CHR_base(t,alpha,eta)+1)*b )
  
  return(uhr)
  
}
```

### Log Likelihood Function of BS Frailty Model (Weibull)

```{r}

log.lik_BS_weibull <- function(par,x,cens){
  
  alpha  <- par[1]
  eta    <- par[2]
  delta  <- par[3]
  bad    <- 1e100

  if (any(!is.finite(c(alpha,eta,delta))) || alpha <= 0 || eta <= 0 || delta <= 0) {
    return(bad)
  }
  
  sf <- unc_sf(t=x,alpha=alpha,eta=eta,delta=delta)
  hz <- unc_hz(t=x,alpha=alpha,eta=eta,delta=delta)

  if (any(!is.finite(sf)) || any(!is.finite(hz)) || any(sf <= 0) || any(hz <= 0)) {
    return(bad)
  }
  
  loglik <- sum(log(sf)) + sum(cens*log(hz))

  if (!is.finite(loglik)) {
    return(bad)
  }
  
  return (-loglik)
}

log.lik_BS_weibullHE <- function(par,y,cens){
  
  loglik <- -log.lik_BS_weibull(par=par,x=y,cens=cens)
  
  return (loglik)
}
```

# Dados

```{r}

data(veteran, package = "survival")

times <- veteran$time
status <- as.numeric(veteran$status == 2) # 0 = censurado e 1 = evento
```

# Estimando - BS frailty Exponential

```{r}

epsilon <- 1e-08

# Chutes iniciais
chuteDelta  <- 1
chuteLambda <- sum(status)/sum(times)

# Estimativas de maxima verossimilhanca
est_BS <- optim(
  par = c(delta=chuteDelta,lambda=chuteLambda),
  fn = log.lik_BS,
  x = times,
  cens = status,
  method = "L-BFGS-B",
  lower = c(delta=epsilon,lambda=epsilon)
)

est_BS$convergence

hatdelta  <- est_BS$par["delta"]
hatlambda <- est_BS$par["lambda"]

print("hatdelta")
hatdelta
print("hatlambda")
hatlambda

loglik_BS <- -est_BS$value
loglik_BS

```

# Estimando - BS frailty Weibull

```{r}

epsilon <- 1e-08

# Chutes iniciais
chuteAlpha <- median(times)
chuteEta   <- 1
chuteDelta <- 1

# Estimativas de maxima verossimilhanca
est_BS_Weibull <- optim(
  par = c(alpha=chuteAlpha,eta=chuteEta,delta=chuteDelta),
  fn = log.lik_BS_weibull,
  x = times,
  cens = status,
  method = "L-BFGS-B",
  lower = c(alpha=epsilon,eta=epsilon,delta=epsilon)
)

est_BS_Weibull$convergence

hatalpha <- est_BS_Weibull$par["alpha"]
hateta   <- est_BS_Weibull$par["eta"]
hatdelta <- est_BS_Weibull$par["delta"]

print("hatalpha")
hatalpha
print("hateta")
hateta
print("hatdelta")
hatdelta

loglik_BS_weibull <- -est_BS_Weibull$value
loglik_BS_weibull

```
